---
title: "Motor Trend Car Road Tests"
author: "The Diamond Team"
date: "2025-07-28"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r mtcars, echo = TRUE} ## Loading the Mt Cars
```
```{r}

```
## Data Exploration by Fidelix and Kaothara

```{r}
### First 6 rows
dim(mtcars) ## we have 32 rows and 11 columns
head(mtcars, 6)
```
```{r}
is.na(mtcars)
sum(is.na(mtcars))
## There is no missing values in the dataset
```
```{r}
summary(mtcars)
```
Hypothesis Testing by Toluwalope and Oluwaseyifunmi
```{r}
#Two-sample t-test for mpg by cylinder groups (4 vs 6)
cat("\n4. Two-sample t-test for mpg (4 cyl vs 6 cyl):\n")
mpg_4cyl <- mtcars$mpg[mtcars$cyl == 4]
mpg_6cyl <- mtcars$mpg[mtcars$cyl == 6]

t_test_result <- t.test(mpg_4cyl, mpg_6cyl)
print(t_test_result)
```
```{r}
# Interpretation
cat("\nInterpretation:\n")
if (t_test_result$p.value < 0.05) {
  cat("With p-value =", t_test_result$p.value, 
      "we reject the null hypothesis. There is a significant difference in mean mpg between 4-cylinder and 6-cylinder cars.\n")
} else {
  cat("With p-value =", t_test_result$p.value, 
      "we fail to reject the null hypothesis. No significant difference in mean mpg between 4-cylinder and 6-cylinder cars.\n")
}
```

```{r}
cat("\n5. One-sample proportion test for automatic transmission:\n")
n_auto <- sum(mtcars$am == 0)
n_total <- nrow(mtcars)
prop_test_result <- prop.test(n_auto, n_total, p = 0.5, correct = FALSE)
print(prop_test_result)
```
```{r}
# Interpretation
cat("\nInterpretation:\n")
if (prop_test_result$p.value < 0.05) {
  cat("With p-value =", prop_test_result$p.value, 
      "we reject the null hypothesis. The proportion of automatic cars is significantly different from 50%.\n")
} else {
  cat("With p-value =", prop_test_result$p.value, 
      "we fail to reject the null hypothesis. The proportion of automatic cars is not significantly different from 50%.\n")
}
```

Correlation Analysis by Aminat and Fidelix
```{r}

```

```{r}

```
Regression Modelling by Yetunde and Ibraheem

```{r}

```
Visualization by Ibraheem and Oluwaseyifunmi
