---
title: "Motor Trend Car Road Tests"
author: "The Diamond Team"
date: "2025-07-28"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r mtcars, echo = TRUE} ## Loading the Mt Cars
```
```{r}

```
## Data Exploration by Fidelix and Kaothara

```{r}
### First 6 rows
dim(mtcars) ## we have 32 rows and 11 columns
head(mtcars, 6)
```
```{r}
is.na(mtcars)
sum(is.na(mtcars))
## There is no missing values in the dataset
```
```{r}
summary(mtcars)
```
Hypothesis Testing by Toluwalope and Oluwaseyifunmi

```{r}

```
Correlation Analysis by Aminat and Fidelix

```{r}

```
Regression Modelling by Yetunde and Ibraheem

```{r}

```
Visualization by Ibraheem and Oluwaseyifunmi
