---
title: "Motor Trend Car Road Tests"
author: "The Diamond Team"
date: "2025-07-28"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r mtcars, echo = TRUE} ## Loading the Mt Cars
```
```{r}
library(corrplot)
```
## Data Exploration by Fidelix and Kaothara

```{r}
### First 6 rows
dim(mtcars) ## we have 32 rows and 11 columns
head(mtcars, 6)
```
```{r}
is.na(mtcars)
sum(is.na(mtcars))
## There is no missing values in the dataset
```
```{r}
summary(mtcars)
```
Hypothesis Testing by Toluwalope and Oluwaseyifunmi
```{r}
#Two-sample t-test for mpg by cylinder groups (4 vs 6)
cat("\n4. Two-sample t-test for mpg (4 cyl vs 6 cyl):\n")
mpg_4cyl <- mtcars$mpg[mtcars$cyl == 4]
mpg_6cyl <- mtcars$mpg[mtcars$cyl == 6]

t_test_result <- t.test(mpg_4cyl, mpg_6cyl)
print(t_test_result)
```
```{r}
# Interpretation
cat("\nInterpretation:\n")
if (t_test_result$p.value < 0.05) {
  cat("With p-value =", t_test_result$p.value, 
      "we reject the null hypothesis. There is a significant difference in mean mpg between 4-cylinder and 6-cylinder cars.\n")
} else {
  cat("With p-value =", t_test_result$p.value, 
      "we fail to reject the null hypothesis. No significant difference in mean mpg between 4-cylinder and 6-cylinder cars.\n")
}
```

```{r}
cat("\n5. One-sample proportion test for automatic transmission:\n")
n_auto <- sum(mtcars$am == 0)
n_total <- nrow(mtcars)
prop_test_result <- prop.test(n_auto, n_total, p = 0.5, correct = FALSE)
print(prop_test_result)
```
```{r}
# Interpretation
cat("\nInterpretation:\n")
if (prop_test_result$p.value < 0.05) {
  cat("With p-value =", prop_test_result$p.value, 
      "we reject the null hypothesis. The proportion of automatic cars is significantly different from 50%.\n")
} else {
  cat("With p-value =", prop_test_result$p.value, 
      "we fail to reject the null hypothesis. The proportion of automatic cars is not significantly different from 50%.\n")
}
```

Correlation Analysis by Aminat and Fidelix
```{r}
# Compute correlation matrix
cat("\n6. Correlation matrix for numerical variables:\n")
cor_matrix <- cor(mtcars)
print(cor_matrix)
```

```{r}
# Visualize correlation matrix with heatmap
cat("\n7. Correlation heatmap:\n")
corrplot(cor_matrix, method = "color", type = "upper", 
         tl.col = "black", tl.srt = 45, addCoef.col = "black")
```

```{r}
# Identify highly correlated variables
cat("\n8. Highly correlated variables (absolute correlation > 0.7):\n")
high_cor <- which(abs(cor_matrix) > 0.7 & abs(cor_matrix) < 1, arr.ind = TRUE)
high_cor_pairs <- data.frame(
  Variable1 = rownames(cor_matrix)[high_cor[,1]],
  Variable2 = colnames(cor_matrix)[high_cor[,2]],
  Correlation = cor_matrix[high_cor]
)
print(high_cor_pairs)
```

Regression Modelling by Yetunde and Ibraheem
```{r}
# Simple linear regression (mpg ~ wt)
cat("\n9. Simple linear regression (mpg ~ wt):\n")
lm_simple <- lm(mpg ~ wt, data = mtcars)
summary(lm_simple)

```


```{r}
# Interpretation
cat("\nInterpretation of simple linear regression:\n")
cat("Regression equation: mpg =", coef(lm_simple)[1], "+", coef(lm_simple)[2], "* wt\n")
cat("For each 1000 lb increase in weight, mpg decreases by", abs(coef(lm_simple)[2]), "on average.\n")
cat("R-squared value of", summary(lm_simple)$r.squared, 
    "means that", round(summary(lm_simple)$r.squared*100, 1), 
    "% of the variability in mpg is explained by weight.\n")
```
```{r}
#Multiple linear regression (mpg ~ wt + hp + cyl)
cat("\n10. Multiple linear regression (mpg ~ wt + hp + cyl):\n")
lm_multiple <- lm(mpg ~ wt + hp + cyl, data = mtcars)
summary(lm_multiple)
```

```{r}
# Interpretation
cat("\nInterpretation of multiple linear regression:\n")
cat("Regression equation: mpg =", coef(lm_multiple)[1], "+", 
    coef(lm_multiple)[2], "* wt +", 
    coef(lm_multiple)[3], "* hp +", 
    coef(lm_multiple)[4], "* cyl\n")
cat("When holding other variables constant:\n")
cat("- For each 1000 lb increase in weight, mpg decreases by", abs(coef(lm_multiple)[2]), "\n")
cat("- For each unit increase in horsepower, mpg decreases by", abs(coef(lm_multiple)[3]), "\n")
cat("- For each additional cylinder, mpg decreases by", abs(coef(lm_multiple)[4]), "\n")
cat("Adjusted R-squared value of", summary(lm_multiple)$adj.r.squared, 
    "means that", round(summary(lm_multiple)$adj.r.squared*100, 1), 
    "% of the variability in mpg is explained by the model.\n")
```
```{r}
# Model comparison
cat("\n11. Model comparison:\n")
cat("Simple model R-squared:", summary(lm_simple)$r.squared, "\n")
cat("Multiple model Adjusted R-squared:", summary(lm_multiple)$adj.r.squared, "\n")
if (summary(lm_multiple)$adj.r.squared > summary(lm_simple)$r.squared) {
  cat("The multiple regression model explains more variance in mpg and is preferred.\n")
} else {
  cat("The simple regression model is sufficient.\n")
}
```

Visualization by Ibraheem and Oluwaseyifunmi
```{r}
```

```
